PDE Solvers for the Laplace's Equation

### 2021-03-18 project/paper/paper.tex
updated paper

\section{Programs}\label{programs}

@@

>>>>

\section{Design and Implementation}\label{programs}

@@

\section{Software and Computing Platform}

This chapter decribes the hardware as well as software used during the development of the implementations of the PDE solvers this paper is based on. The purpose of this is for the reader to get a grasp on if the result in the chapter following this is reasonable.

The implementaions were developed on a Intel(R) Core(TM) i5-8250U CPU @ 1.60GHz computer with eight Gb of RAM. The operating system used was Ubuntu 20.04.2 LTS and the developement environment used was Visual Studio Code.
